\large{Vipassana for Hackers} \\ \Huge{Paper Three: Why Meditate?} \\ \large\textit{Version 0.1}

### 2020-05-08 paper-three/paper-three.tex
p3: gratitude

\begin{itemize}
  \item posture
  \item sleep
  \item digestion (``Make sure to pay attention to your poops!'' first course)
  \item diet
  \item schedule
  \item health (activation / motivation)
  \item ethics (activation / motivation)
  \item your children: a. knowing how to meditate, b. cross-legged posture
  \item emotion (i.e. anger)
  \item dealing with death
  \item mundane sphere / productivity (21 lessons, seinfeld)
  \item unlearning obsessive / repetitive thought, enhancing creativity
  \item controlling unbounded sexuality without repression (louis c.k. joke?)
  \item clarity: in thought, work, planning
  \item Die Standing Up
  \item \url{https://www.pnas.org/content/early/2019/10/18/1909959116}
\end{itemize}

>>>>

\begin{itemize}
  \item posture
  \item sleep
  \item digestion (``Make sure to pay attention to your poops!'' first course)
  \item diet
  \item schedule
  \item health (activation / motivation)
  \item ethics (activation / motivation)
  \item your children: a. knowing how to meditate, b. cross-legged posture
  \item emotion (i.e. anger)
  \item gratitute (gratitude vs. fear; julie) - https://youtu.be/WPPPFqsECz0
  \item dealing with death
  \item mundane sphere / productivity (21 lessons, seinfeld)
  \item unlearning obsessive / repetitive thought, enhancing creativity
  \item controlling unbounded sexuality without repression (louis c.k. joke?)
  \item clarity: in thought, work, planning
  \item federated, p2p, distributed systems like blockchain / holochain attempt to circumvent
    structures of oppression and control -- what if corporations could be rebuilt from inside,
    one employee/stakeholder at a time such that ethics were inherent to the company's very
    existence?
  \item Die Standing Up
  \item \url{https://www.pnas.org/content/early/2019/10/18/1909959116}
\end{itemize}
